MITM: Logging a Bluetooth Keyboard

### 2013-03-15 final_paper/paper.tex
Adding mitigation content

\section{Mitigation}
\section{Future Work}
\section{Conclusions}

>>>>

\section{Mitigation}
We are proposing three countermeasures to prevent against Man in the Middle attacks on Bluetooth keyboards.

\begin{enumerate}
\item Stay out of discoverable mode as much as possible. This way any attacker would need special hardware to perform any kind of fancy attack and take much longer to actually find the keyboards Bluetooth address.
\item Keyboards should require 
\item Pair with keyboard and victim
\end{enumerate}

No disco mode
Keyboards should force pins to be used, more sensitive than keyboards
Bluetooth managers should be smarter

\section{Future Work}

\section{Conclusions}
